### 2018-09-16 Sections/network_algorithms.tex
fig updaste

\startnormtable
\begin{table*}[!htbp]
	\begin{tabular}{|c|c|c|c|}
		\hline
  		\rowcolor{Dandelion} Algorithm & Description & Complexity class & Scaling \\
  		\hline
  		\hline
  		\rowcolor{LimeGreen} Breadth-first-search & Explore all vertices in a graph & \textbf{P} & $O(|V|+|E|)$ \\
  		\hline
  		\rowcolor{LimeGreen} Depth-first-search & (same as above) & \textbf{P} & $O(|V|+|E|)$ \\
		\hline
  		\rowcolor{LimeGreen} Shortest-path (Dijkstra) & Find the shortest route between two nodes & \textbf{P} & $O(|V|^2)$ \\
  		\rowcolor{LimeGreen} & in a directed graph & &  \\
  		  		\hline
		\rowcolor{LimeGreen} Shortest-path (\textit{A*}) & (same as above) & \textbf{P} & (varying) \\
  		  		\hline
		\rowcolor{LimeGreen} Single-source shortest path & Find the shortest paths from a given node to & \textbf{P} & $O(|V|\cdot |E|)$\\
  		\rowcolor{LimeGreen} & \textit{all} other nodes & & \\
 		\hline
		\rowcolor{LimeGreen} Minimum spanning tree & Find a spanning tree of a graph that minimises & \textbf{P} & $O(|E|\log |V|)$ \\
  		\rowcolor{LimeGreen} & the total of the edge weights & & \\
  		\hline
  		\rowcolor{LimeGreen} Minimum cost flow & Minimise total costs in a network &  \textbf{P} & $O(|V|\log |V|(|E|$\\
  		\rowcolor{LimeGreen} (Orlin) & with a specified amount of flow& & $+|V|\log |V|))$ \\
  		\hline
  		\rowcolor{LimeGreen} Maximum flow & Maximise flow in a network, regardless of costs & \textbf{P} & $O(|E|\cdot c_\mathrm{max})$ \\
  		\rowcolor{LimeGreen} (Ford-Fulkerson) & & & \\
  		\hline
  		\rowcolor{Lavender} Multi-commodity flow & Same as maximum flow, but generalised to & \textbf{NP}-complete & ? \\
  		\rowcolor{Lavender} & arbitrary numbers of users & (exactly), & \\
  		\rowcolor{Lavender} & & \textbf{P} (approximation & \\
  		\rowcolor{Lavender} & & using heuristics) & \\
  		\hline
  		\rowcolor{Lavender} Vehicle routing problem & Generalises the shortest-path algorithm to multiple & \textbf{NP}-complete & ? \\
  		\rowcolor{Lavender} & users, with distinct sources and destinations & & \\ 
  		\hline
  		\rowcolor{Lavender} Vehicle rescheduling problem & Same as above but with dynamically changing costs & \textbf{NP}-complete & ? \\
    	\hline
	\end{tabular}
	\captionspacetab \caption{Summary of some important network algorithms and their complexities. The \textbf{NP}-complete algorithms are not believed to have efficient classical algorithms, and their exact scaling is not well understood.} \label{tab:net_alg_sum} \index{Network algorithms}\index{Breadth-first-search (BFS) algorithm}\index{Depth-first-search (DFS) algorithm}\index{Shortest-path algorithm}\index{Single-source shortest path algorithm}\index{Minimum spanning tree algorithm}\index{Minimum cost flow algorithm}\index{Maximum flow algorithm}\index{Multi-commodity flow algorithm}\index{Vehicle routing problem}\index{Vehicle rescheduling problem}
\end{table*}
\startalgtable

@@

\if 2\pubmode
	\begin{figure}[!htbp]
	\includegraphics[width=0.3\textwidth]{BFS_DFS_long}
	\captionspacefig \caption{Comparison of the order in which vertices are explored, using the breadth-first-search (BFS) and depth-first-search (DFS) algorithms, where vertex 1 is the root vertex.} \label{fig:BFS_DFS}
	\end{figure}
\else
	\begin{figure*}[!htbp]
	\includegraphics[width=0.65\textwidth]{BFS_DFS}
	\captionspacefig \caption{Comparison of the order in which vertices are explored, using the breadth-first-search (BFS) and depth-first-search (DFS) algorithms, where vertex 1 is the root vertex.} \label{fig:BFS_DFS}
	\end{figure*}
\fi

@@

Fig.~\ref{fig:simp_route_opt} illustrates a directed, edge-weighted graph. A shortest-path algorithm applied between vertices $A$ and $B$ would return \mbox{$R_\mathrm{shortest} = A\to F\to B$} as the minimum cost route.

@@

\if 2\pubmode
\begin{figure}[!htbp]
\includegraphics[width=0.35\textwidth]{constrained_shortest_path_long}
\caption{Example of a constrained shortest-path algorithm. Beginning with the initial graph we eliminate edges that do not satisfy imposed nearest-neighbour constraints. This is performed as a pre-processing stage. Then a usual shortest-path algorithm is applied to the reduced graph, yielding the optimal route subject to the required constraints.}\label{fig:constrained_shortest_path}
\end{figure}
\else
\begin{figure*}[!htbp]
\includegraphics[width=\textwidth]{constrained_shortest_path}
\caption{Example of a constrained shortest-path algorithm. Beginning with the initial graph we eliminate edges that do not satisfy imposed nearest-neighbour constraints. This is performed as a pre-processing stage. Then a usual shortest-path algorithm is applied to the reduced graph, yielding the optimal route subject to the required constraints.}\label{fig:constrained_shortest_path}
\end{figure*}
\fi

@@

%
% Minimum Cost Flow
%

\subsection{Minimum cost flow} \label{sec:min_cost_flow_prob} \index{Minimum cost flow algorithm}

The \textit{minimum cost flow problem} \cite{???} is that of minimising costs through a network for a specified amount of flow (i.e total bandwidth or throughput), which acts as a constraint on the problem. The definition of `cost' in this context is compatible with our earlier definition of cost metrics (Def.~\ref{def:metric}).

@@

\begin{figure}[!hbtp]
\includegraphics[width=0.3\textwidth]{vehicle_routing_alg}
	\caption{Example of the vehicle routing problem, the multi-user generalisation of the shortest-path problem, where the goal is to minimise the total cost across all users. Intuitively, because whenever individual shortest-paths intersect one must trial different prioritisations, the combinatorics of this grow exponentially with the number of competing users.}\label{fig:VRS}
\end{figure}

>>>>

\startnormtable
\begin{table*}[!htbp]
	\begin{tabular}{|c|c|c|c|}
		\hline
  		\rowcolor{Dandelion} Algorithm & Description & Complexity class & Scaling \\
  		\hline
  		\hline
  		\rowcolor{LimeGreen} Breadth-first-search & Explore all vertices in a graph & \textbf{P} & $O(|V|+|E|)$ \\
  		\hline
  		\rowcolor{LimeGreen} Depth-first-search & (same as above) & \textbf{P} & $O(|V|+|E|)$ \\
		\hline
  		\rowcolor{LimeGreen} Shortest-path (Dijkstra) & Find the shortest route between two nodes & \textbf{P} & $O(|V|^2)$ \\
  		\rowcolor{LimeGreen} & in a directed graph & &  \\
  		  		\hline
		\rowcolor{LimeGreen} Shortest-path (\textit{A*}) & (same as above) & \textbf{P} & (varying) \\
  		  		\hline
		\rowcolor{LimeGreen} Single-source shortest path & Find the shortest paths from a given node to & \textbf{P} & $O(|V|\cdot |E|)$\\
  		\rowcolor{LimeGreen} & \textit{all} other nodes & & \\
 		\hline
		\rowcolor{LimeGreen} Minimum spanning tree & Find a spanning tree of a graph that minimises & \textbf{P} & $O(|E|\log |V|)$ \\
  		\rowcolor{LimeGreen} & the total of the edge weights & & \\
  		\hline
  		\rowcolor{LimeGreen} Minimum-cost flow & Minimise total costs in a network &  \textbf{P} & $O(|V|\log |V|(|E|$\\
  		\rowcolor{LimeGreen} (Orlin) & with a specified amount of flow& & $+|V|\log |V|))$ \\
  		\hline
  		\rowcolor{LimeGreen} Maximum flow & Maximise flow in a network, regardless of costs & \textbf{P} & $O(|E|\cdot c_\mathrm{max})$ \\
  		\rowcolor{LimeGreen} (Ford-Fulkerson) & & & \\
  		\hline
  		\rowcolor{Lavender} Multi-commodity flow & Same as maximum flow, but generalised to & \textbf{NP}-complete & ? \\
  		\rowcolor{Lavender} & arbitrary numbers of users & (exactly), & \\
  		\rowcolor{Lavender} & & \textbf{P} (approximation & \\
  		\rowcolor{Lavender} & & using heuristics) & \\
  		\hline
  		\rowcolor{Lavender} Vehicle routing problem & Generalises the shortest-path algorithm to multiple & \textbf{NP}-complete & ? \\
  		\rowcolor{Lavender} & users, with distinct sources and destinations & & \\ 
  		\hline
  		\rowcolor{Lavender} Vehicle rescheduling problem & Same as above but with dynamically changing costs & \textbf{NP}-complete & ? \\
    	\hline
	\end{tabular}
	\captionspacetab \caption{Summary of some important network algorithms and their complexities. The \textbf{NP}-complete algorithms are not believed to have efficient classical algorithms, and their exact scaling is not well understood.} \label{tab:net_alg_sum} \index{Network algorithms}\index{Breadth-first-search (BFS) algorithm}\index{Depth-first-search (DFS) algorithm}\index{Shortest-path algorithm}\index{Single-source shortest path algorithm}\index{Minimum spanning tree algorithm}\index{Minimum-cost flow algorithm}\index{Maximum flow algorithm}\index{Multi-commodity flow algorithm}\index{Vehicle routing problem}\index{Vehicle rescheduling problem}
\end{table*}
\startalgtable

@@

\if 2\pubmode
	\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.3\textwidth]{BFS_DFS_long}
	\captionspacefig \caption{Comparison of the order in which vertices are explored, using the breadth-first-search (BFS) and depth-first-search (DFS) algorithms, where vertex 1 is the root vertex.} \label{fig:BFS_DFS}
	\end{figure}
\else
	\begin{figure*}[!htbp]
	\includegraphics[clip=true, width=0.65\textwidth]{BFS_DFS}
	\captionspacefig \caption{Comparison of the order in which vertices are explored, using the breadth-first-search (BFS) and depth-first-search (DFS) algorithms, where vertex 1 is the root vertex.} \label{fig:BFS_DFS}
	\end{figure*}
\fi

@@

Fig.~\ref{fig:simp_route_opt} illustrates a directed, edge-weighted graph. A shortest-path algorithm applied between vertices $A$ and $B$ would return \mbox{$R_\mathrm{shortest} = A\to F\to B$} as the minimum-cost route.

@@

\if 2\pubmode
\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.35\textwidth]{constrained_shortest_path_long}
\caption{Example of a constrained shortest-path algorithm. Beginning with the initial graph we eliminate edges that do not satisfy imposed nearest-neighbour constraints. This is performed as a pre-processing stage. Then a usual shortest-path algorithm is applied to the reduced graph, yielding the optimal route subject to the required constraints.}\label{fig:constrained_shortest_path}
\end{figure}
\else
\begin{figure*}[!htbp]
\includegraphics[clip=true, width=\textwidth]{constrained_shortest_path}
\caption{Example of a constrained shortest-path algorithm. Beginning with the initial graph we eliminate edges that do not satisfy imposed nearest-neighbour constraints. This is performed as a pre-processing stage. Then a usual shortest-path algorithm is applied to the reduced graph, yielding the optimal route subject to the required constraints.}\label{fig:constrained_shortest_path}
\end{figure*}
\fi

@@

%
% Minimum-Cost Flow
%

\subsection{Minimum-cost flow} \label{sec:min_cost_flow_prob} \index{Minimum-cost flow algorithm}

The \textit{minimum-cost flow problem} \cite{???} is that of minimising costs through a network for a specified amount of flow (i.e total bandwidth or throughput), which acts as a constraint on the problem. The definition of `cost' in this context is compatible with our earlier definition of cost metrics (Def.~\ref{def:metric}).

@@

\begin{figure}[!hbtp]
\includegraphics[clip=true, width=0.35\textwidth]{vehicle_routing_alg}
	\caption{Example of the vehicle routing problem, the multi-user generalisation of the shortest-path problem, where the goal is to minimise the total cost across all users. Intuitively, because whenever individual shortest-paths intersect one must trial different prioritisations, the combinatorics of this grow exponentially with the number of competing users.}\label{fig:VRS}
\end{figure}

### 2018-09-16 Sections/protocols_for_the_quantum_internet.tex
minor

Achieving the SNL is easily done using a Mach-Zehnder interferometer (Sec.~\ref{sec:MZ_inter}) fed with coherent states (Sec.~\ref{sec:coherent_states}), which are not true quantum states. Referring to Fig.~\ref{fig:MZ_inter}, if a coherent state is inputted into one arm of the interferometer, with no phase-shift (\mbox{$\tau=0$}) all the coherent amplitude would exit the corresponding output port. If on the other hand there were a $\pi$ phase-shift, all the amplitude would exit the other output port. For intermediate $\tau$ there will be varying degrees of coherent amplitude distributed between the two outputs. Thus, the relative amplitude exiting the two output ports acts as a signature for the internal phase-shift.

@@

Experimentally, there have been several demonstrations of the protocol, albeit at relatively short distances. Continuous time-bin\index{Time-bin encoding} entangled photons were used as the entanglement resource to obtain a time-correlation between a distance of 3km \cite{bib:valencia2004distant}, and another technique based on Hong-Ou-Mandel interferometry\index{Hong-Ou-Mandel (HOM) interferometry} was performed across a 4km fibre link \cite{bib:quan2016demonstration}. Several other demonstrations based on nuclear magnetic resonance (NMR)\index{Nuclear magnetic resonance} \cite{bib:zhang2004nuclear, bib:kong2017implementation} have also been performed.

There are however several outstanding problems with the quantum clock synchronisation scheme as presented above. In the scheme of Jozsa \textit{et al.}, if one starts in a perfect singlet state\index{Bell states}, the scheme works as intended, but if one instead starts with the state, 
\begin{align}
\frac{1}{\sqrt{2}} ( | 0 \rangle_A | 1 \rangle_B - e^{i \delta} | 1 \rangle_A | 0 \rangle_B ),
\end{align}
(a Bell pair augmented by a local phase) one obtains an offset to the synchronisations between the two parties. In practice, such a phase could arise from decoherence induced noise, or differences in the basis conventions chosen by the two parties. Thus, in practice entanglement purification\index{Entanglement purification} would be required to produce a singlet state with \mbox{$\delta=0$} prior to executing the protocol. However, it was argued that to perform the entanglement purification quantum circuit correctly, the timing of the quantum gates would need to be controlled, which requires synchronised clocks \cite{bib:preskill2000quantum} --  this renders syncrhonisation impossible. It has previously been shown that such a phase cannot be eliminated using asynchronous entanglement purification\index{Entanglement purification} \cite{bib:yurtsever02}, and hence the protocol remains incomplete in the general case where imperfect singlet pairs\index{Bell states} are shared.

>>>>

Achieving the SNL is easily done using a Mach-Zehnder interferometer (Sec.~\ref{sec:MZ_inter}) fed with coherent states (Sec.~\ref{sec:coherent_states}), which are not true quantum states. Referring to Fig.~\ref{fig:MZ_inter}, if a coherent state is inputted into one arm of the interferometer, with no phase-shift (\mbox{$\tau=0$}) all the coherent amplitude would exit the corresponding output port. If on the other hand there were a $\pi$ phase-shift, all the amplitude would exit the other output port. For intermediate $\tau$ there will be varying degrees of coherent amplitude distributed between the two outputs. Thus, the relative amplitude exiting the two output ports acts as a signature for the internal phase-shift $\tau$.

@@

Experimentally, there have been several demonstrations of the protocol, albeit at relatively short distances. Continuous time-bin\index{Time-bin encoding} entangled photons were used as the entanglement resource to obtain a time-correlation between a distance of 3km \cite{bib:valencia2004distant}, and another technique based on Hong-Ou-Mandel interferometry\index{Hong-Ou-Mandel (HOM) interference} was performed across a 4km fibre link \cite{bib:quan2016demonstration}. Several other demonstrations based on nuclear magnetic resonance (NMR)\index{Nuclear magnetic resonance} \cite{bib:zhang2004nuclear, bib:kong2017implementation} have also been performed.

There are however several outstanding problems with the quantum clock synchronisation scheme as presented above. In the scheme of Jozsa \textit{et al.}, if one starts in a perfect singlet state\index{Bell states}, the scheme works as intended, but if one instead starts with the state, 
\begin{align}
\frac{1}{\sqrt{2}} ( | 0 \rangle_A | 1 \rangle_B - e^{i \delta} | 1 \rangle_A | 0 \rangle_B ),
\end{align}
(a Bell pair augmented by a local phase) one obtains an offset to the synchronisations between the two parties. In practice, such a phase could arise from decoherence induced noise, or differences in the basis conventions chosen by the two parties. Thus, in practice entanglement purification\index{Entanglement purification} would be required to produce a singlet state with \mbox{$\delta=0$} prior to executing the protocol. However, it was argued that to perform the entanglement purification quantum circuit correctly, the timing of the quantum gates would need to be controlled, which requires synchronised clocks \cite{bib:preskill2000quantum} --  this renders synchronisation impossible. It has previously been shown that such a phase cannot be eliminated using asynchronous entanglement purification\index{Entanglement purification} \cite{bib:yurtsever02}, and hence the protocol remains incomplete in the general case where imperfect singlet pairs\index{Bell states} are shared.
